---
title: "HW 6 for P8105 - hlz2108"
author: "Helen Zhang"
date: "November 24, 2020"
output: github_document
---
Below is the code for setup:

```{r setup}
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
library(p8105.datasets)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 0

This “problem” focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files.

## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
model_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
    ) %>%
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

```{r}
model_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>% 
  view

birthweight_df

purrr::map(birthweight_df, ~ sum(is.na(.)))
```

This dataset contains `r nrow(birthweight_df)` rows and `r ncol(birthweight_df)` columns, there is no missing data.

For the regression model, I chose several hypothesized variables that I believe may affect birthright along with variables that have be determined from previous research and literature.

A quick Google search lead me to this Wikipedia article [https://en.wikipedia.org/wiki/Low_birth_weight], which indicated that several risk factors in the mother that may contribute to low birth weight include young ages, multiple pregnancies (parity), and previous LBW infants. As such, I included mom age, parity, and previous number of low birthweight infants in the model.

Gestational weeks and presence of malformations appear to be an logical indicator of birthweight and was included in the model as such. 

I was also interested in whether several socialdemographic factors would affect birthweight, so I included factors such as mom's race and financial income.

```{r regression_model_1}
model_fit_1 = lm(bwt ~ gaweeks + momage + mrace + malform + parity + fincome + pnumlbw, data = birthweight_df)
```

```{r residual_plot}
birthweight_df %>% 
  modelr::add_residuals(model_fit_1) %>%
  modelr::add_predictions(model_fit_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(se = F, color = "red", method = "lm")
  labs(
    title = "Predicted vs. Residuals",
    x = "Predicted",
    y = "Residuals"
    ) +
  theme(plot.title = element_text(hjust = 0.5))
```

### Fit other models.

```{r model_building}
model_2 = lm(bwt ~ gaweeks + blength, data = birthweight_df)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_df)
```

### Cross Validaton:

```{r cv_df, warning=FALSE}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
   model_fit_1 = map(.x = train, ~lm(bwt ~ gaweeks + momage + mrace + malform + parity + fincome + pnumlbw, data = .x)),
   model_2 = map(.x = train, ~lm(bwt ~ gaweeks + blength, data = .x)),
   model_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(.x = model_fit_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(.x = model_3, .y = test, ~rmse(model = .x, data = .y))
  )
```

### Violin plot of RMSEs

```{r violin_plot}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

From the RMSE plot, it appears that of the 3 models, model 3 is the best fit as it has the lowest RSME. As expected, the model 1 (the model generated from Wikipedia knowledge) was a poor fit for the data and it is best not to rely on Wikipedia information.

Model 3 contains head circumference, length, sex, and all interactions (including the three-way interaction) between these. 

## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r bootsample}
boot_sample = function(df) {

  sample_frac(df, replace = TRUE)

}
```

```{r bootstrapping}
boot_straps = 
  data_frame(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )

boot_results = 
  boot_straps %>% 
  mutate(
    models = map(.x = strap_sample, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::glance)
  ) %>%
  select(strap_number, results) %>% 
  unnest(results)
```

### R-Squared

```{r r_squared}
boot_results %>%
  ggplot(aes(x = adj.r.squared)) +
  geom_density() +
  labs(
        title = "Distribution of R Squared",
        x = "R Squared"
    ) +
  theme(plot.title = element_text(hjust = 0.5))
```

The distribution of R squared appears to follow a normal distribution, centered around ~0.912.

The 95% CI of adjusted R square is (`r quantile(boot_results$adj.r.squared, probs=0.025)`, `r quantile(boot_results$adj.r.squared, probs=0.975)`).

### Log Function

```{r second_bootstrap}
second_bootstrap = weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(term, estimate) %>%
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  unnest(cols = c(`(Intercept)`, tmin)) %>%
  rename(
    beta_0 = "(Intercept)",
    beta_1 = tmin
  ) %>% 
 mutate(
    log_fx = log(beta_0*beta_1)
  )
```

```{r log_plot}
second_bootstrap %>%
  ggplot(aes(x = log_fx)) +
  geom_density() +
  labs(
        title = "Distribution of Log Function",
        x = "Log Function"
    ) +
  theme(plot.title = element_text(hjust = 0.5))
```

The log function plot also appears to follow a normal distribution, centered around ~2.015.

The 95% CI of adjusted R square is (`r quantile(second_bootstrap$log_fx, probs=0.025)`, `r quantile(second_bootstrap$log_fx, probs=0.975)`).