---
title: "HW 6 for P8105 - hlz2108"
author: "Helen Zhang"
date: "November 24, 2020"
output: github_document
---
Below is the code for setup:

```{r setup}
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
library(p8105.datasets)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 0

This “problem” focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files.

## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
model_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
    ) %>%
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

```{r}
model_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  view
```


```{r}
model_fit = lm(bwt ~ gaweeks, data = birthweight_df)

birthweight_df %>% 
  modelr::add_residuals(model_fit) %>% 
  ggplot(aes(x = gaweeks, y = resid)) + 
  geom_point()
```

Copy cross-validation code

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.



## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The bootstrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data:

r̂ 2
log(β̂ 0∗β̂ 1)
Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quartiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). Note: broom::glance() is helpful for extracting r̂ 2 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β̂ 0∗β̂ 1).

