---
title: "HW 6 for P8105 - hlz2108"
author: "Helen Zhang"
date: "November 24, 2020"
output: github_document
---
Below is the code for setup:

```{r setup}
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
library(p8105.datasets)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 0

This “problem” focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files.

## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
model_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
    ) %>%
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

```{r}
model_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>% 
  view

birthweight_df

purrr::map(birthweight_df, ~ sum(is.na(.)))
```

This dataset contains `r nrow(birthweight_df)` rows and `r ncol(birthweight_df)` columns, there is no missing data.

For the regression model, I chose several hypothesized variables that I believe may affect birthright along with variables that have be determined from previous research and literature.

A quick Google search lead me to this (Wikipedia)[https://en.wikipedia.org/wiki/Low_birth_weight] article, which indicated that several risk factors in the mother that may contribute to low birth weight include young ages, multiple pregnancies (parity), and previous LBW infants. As such, I included mom age, parity, and previous number of low birthweight infants in the model.

Gestational weeks and presence of malformations appear to be an logical indicator of birthweight and was included in the model as such. 

I was also interested in whether several socialdemographic factors would affect birthweight, so I included factors such as mom's race and financial income.

```{r regression_model_1}
model_fit_1 = lm(bwt ~ gaweeks + momage + mrace + malform + parity + fincome + pnumlbw, data = birthweight_df)
```


```{r residual_plot}
birthweight_df %>% 
  modelr::add_residuals(model_fit_1) %>%
  modelr::add_predictions(model_fit_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(se = F, color = "red", method = "lm")
  labs(
    title = "Predicted vs. Residuals",
    x = "Predicted",
    y = "Residuals"
    ) +
  theme(plot.title = element_text(hjust = 0.5))
```

Fit other models.

```{r model_building}
model_2 = lm(bwt ~ gaweeks + blength, data = birthweight_df)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_df)
```

Cross Validaton:

```{r cv_df}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
   model_fit_1 = map(.x = train, ~lm(bwt ~ gaweeks + momage + mrace + malform + parity + fincome + pnumlbw, data = .x)),
   model_2 = map(.x = train, ~lm(bwt ~ gaweeks + blength, data = .x)),
   model_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(.x = model_fit_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(.x = model_3, .y = test, ~rmse(model = .x, data = .y))
  )
```

Violin plot of RMSEs

```{r violin_plot}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

From the RMSE plot, it appears that model 3 is the best fit as it has the lowest RSME. 

Model 3 contains head circumference, length, sex, and all interactions (including the three-way interaction) between these.

## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The bootstrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data:

r̂ 2
log(β̂ 0∗β̂ 1)
Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quartiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). 

Note: broom::glance() is helpful for extracting r̂ 2 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β̂ 0∗β̂ 1).

